Irt plot extra

### 2022-02-10 manuscript.Rmd
Participants Map

```{r rafel, include=F}
# In addition to the LEBA questionnaire, which is subject of the current study, we assessed other variables and items which were not included in the present analysis. This comprised various sleep-related measures, i.e., sleep disturbances and sleep-related impairment (adult and pediatric versions) [@Bevans.2019; @Buysse.2010; @Forrest.2018; @Harb.2015; @Yu.2011], sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration [MCTQ version for adults and adolescents @roenneberg2003life] plus sleep environment [@Olivier.2016]. Furthermore, we included a light sensitivity questionnaire (photophobia vs. photophilia) [@Wu.2017] and self-reported pubertal stage assessment [@Petersen.1988] for participants younger than 18 years of age. Moreover, we incorporated custom items on meal timing and caffeine consumption in the “workday vs. free day” structure of the MCTQ sleep-wake regulation. Example items are: “On workdays I usually have my first meal at __:__”, “On free days I usually have my last meal at __:__”, and “On workdays I usually drink my first caffeinated drink at __:__”.

@@

num.countries <- unique(TZ$V1)
num.Timezone <- unique(TZ$V2)

UTC <- as.data.frame(str_split_fixed(TZ$V2, "UTC", 2))
numUTC <- unique(UTC$V2)
```

@@

@@

A quantitative cross-sectional fully anonymous online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch). Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) of a Comic co-released with the survey[@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux]. The landing page of the on-line survey had the explanatory statements It was mentioned in the explanatory statement that their participation was voluntary and that they could withdraw from participation anytime without being penalized. At the beginning of the survey, for the adult participants (>18 years) consent was recorded digitally. Underaged participants (<18 years) were urged to obtain assent from their parents/legal guardians, before filling in the survey. The survey took around 15 to 20 minutes for which they were not compensated. As a part of the demographics participants provided information regarding age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language as single-item demographic variables. The demographic characteristics of our sample are given in Table \@ref(tab:demotab).To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention. What is 4+5?"). Participants needed to confirm that they were participating the survey for the first time. 
Questions incorporating retrospective recall were all aligned to the period of "past four weeks". The data analysed in this study was collected between 17 May 2021 and 3 September 2021. 
```{r demotab, warning=F, message=F}
desc_kable  %>% kable_styling(latex_options = c("scale_down")) %>% landscape()
```

@@

By reason of using fully anonymous online survey data, the present research project does not fall under the scope of the Human Research Act, making an authorisation from the ethics committee redundant. Nevertheless, the cantonal ethics commission (Ethikkommission Nordwest- und Zentralschweiz, EKNZ) reviewed our proposition (project ID Req-2021-00488) and issued an official clarification of responsibility (full document see Suppl. X in appendix).

@@

After reviewing the literature, we identified several light exposure related scale. However, no scales specifically measuring the behavioural component of light exposure were found. As such ,we developed a comprehensive item pool of 48 items with six point Likert response scale (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always).The whole list of 48 items were then judged  based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by an expert panel. The expert panel composed of all authors and researchers from the fields of chronobiology, light research, neuroscience and psychology. The panel members independently judged each of the items in terms of their relevance and representativeness and suggested required modification, if there is any. The author team acknowledged the auggestions and amended the items as required thus creating a 48-item scale

@@

Table \@ref(tab:demotab) summarizes the survey participants' demographic characteristics. Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses. (XX??) participants were excluded from analysis due to not passing at least one of the "attention check" items. For exploring initial factor structure (EFA), a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]. For estimating the sample size for the confirmatory factor analysis (CFA) we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per parameter is required to earn trustworthiness of the result. Our sample size exceeds these requirements: Anonymous responses from a total of *n* = `r nrow(desctable.data)` participants were included in the analysis of the current study, split into samples for exploratory (EFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "1. EFA Sample",])`) and confirmatory factor analysis (CFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "2. CFA Sample",])`). The EFA sample included participants filling out the questionnaire from 17 May 2021 to XX XXX 2021, whereas participants who filled out the questionnaire from YY YYY 2021 to 3 September 2021 were included in the CFA analysis. Participants indicated filling out the online survey from a diverse range of geographic locations. The ten most common country and time zone combinations included:

>>>>

```{r rafel, eval=FALSE, include=FALSE}
# In addition to the LEBA questionnaire, which is subject of the current study, we assessed other variables and items which were not included in the present analysis. This comprised various sleep-related measures, i.e., sleep disturbances and sleep-related impairment (adult and pediatric versions) [@Bevans.2019; @Buysse.2010; @Forrest.2018; @Harb.2015; @Yu.2011], sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration [MCTQ version for adults and adolescents @roenneberg2003life] plus sleep environment [@Olivier.2016]. Furthermore, we included a light sensitivity questionnaire (photophobia vs. photophilia) [@Wu.2017] and self-reported pubertal stage assessment [@Petersen.1988] for participants younger than 18 years of age. Moreover, we incorporated custom items on meal timing and caffeine consumption in the “workday vs. free day” structure of the MCTQ sleep-wake regulation. Example items are: “On workdays I usually have my first meal at __:__”, “On free days I usually have my last meal at __:__”, and “On workdays I usually drink my first caffeinated drink at __:__”.

@@

num.countries <- as.data.frame(unique(TZ$V1))
num.Timezone <- unique(TZ$V2)

UTC <- as.data.frame(str_split_fixed(TZ$V2, "UTC", 2))
numUTC <- as.data.frame(unique(UTC$V2))
nrow(numUTC)
```

@@

```{r participantmap, include =F}

countries <- as.data.frame(tz_tibble[,1])
countries <- as.data.frame(countries[-1,])

colnames(countries) <- "TZ"
countries.2 <- as.data.frame(str_split_fixed(countries$TZ, "-", 2))
countries.2[ ,1][ countries.2[ , 1 ] == "United States " ] <- "USA"
countries.2[ ,1][ countries.2[ , 1 ] == "United Kingdom " ] <- "UK"
countries.2[ ,1][ countries.2[ , 1 ] == "Germany " ] <- "Germany"
countries.2[ ,1][ countries.2[ , 1 ] == "India "  ] <- "India" 
countries.2[ ,1][ countries.2[ , 1 ] == "France "  ] <- "France" 
countries.2[ ,1][ countries.2[ , 1 ] == "Switzerland " ] <- "Switzerland"
countries.2[ ,1][ countries.2[ , 1 ] == "Brazil "  ] <- "Brazil"
countries.2[ ,1][ countries.2[ , 1 ] == "Netherlands " ] <- "Netherlands"
countries.2[ ,1][ countries.2[ , 1 ] == "Canada "  ] <- "Canada" 
countries.2[ ,1][ countries.2[ , 1 ] == "Poland " ] <- "Poland"

country_name <- as.data.frame(unique(countries.2[,1]))
country_name.2 <- (country_name[1:10,])

thismap = map_data("world")

# Set colors
colors <- scales::hue_pal()(10)
thismap <- mutate(thismap, fill = ifelse(region %in% country_name.2, 
                                         sample(colors, 10), "white"))
thismap <- within(thismap, fill[region == 'Canada'] <- '#FF62BC')
thismap <- within(thismap, fill[region == 'Brazil'] <- '#D89000')
thismap <- within(thismap, fill[region == 'USA'] <- '#00BFC4')
thismap <- within(thismap, fill[region == 'UK'] <- 'blue')
thismap <- within(thismap, fill[region == 'Germany'] <- 'Green')
thismap <- within(thismap, fill[region == 'Netherlands'] <- '#A3A500')
thismap <- within(thismap, fill[region == 'Poland'] <- 'Pink')
thismap <- within(thismap, fill[region == 'France'] <- 'Orange')
thismap <- within(thismap, fill[region == 'Switzerland'] <- 'purple')

label.data <-thismap[thismap$region %in% country_name.2,]

USA <- subset(label.data, region == "USA")
UK <- subset(label.data, region == "UK")
Germany <- subset(label.data, region == "Germany")
India <- subset(label.data, region == "India")
France <- subset(label.data, region == "France")
Switzerland <- subset(label.data, region == "Switzerland")
Brazil <- subset(label.data, region == "Brazil")
Netherlands <- subset(label.data, region == "Netherlands")
Canada <- subset(label.data, region == "Canada")
Poland <- subset(label.data, region == "Poland")

label.data.2 <- rbind(USA[386,],UK[1,],Germany[1,],India[327,],France[1,],
                      Switzerland[1,],Brazil[33,],Netherlands[1,],Canada[5000,],Poland[1,])

label.data.2[1,1] <- -100
label.data.2[1,2] <- 40
label.data.2[2,2] <- 52
label.data.2[9,2] <- 55
label.data.2[7,2] <- -9
label.data.2[7,1] <- -48
label.data.2[4,2] <- 25
label.data.2[4,1] <- 84

label.data.2[5,2] <- 46
label.data.2[5,1] <- 6
label.data.2[8,2] <- 51

distribution <- ggplot(thismap, aes(long, lat, fill = fill, group=group)) + 
  geom_polygon(colour="gray", size =.3) +  
  scale_fill_identity()+apatheme+ theme(
    axis.text.x = element_blank(),
                                        axis.text.y = element_blank(),
                                        axis.title.x = element_blank(),
                                        axis.title.y = element_blank(),
                                        plot.title = element_blank(),
                                        axis.line.x = element_blank(),
                                        axis.line.y = element_blank(),
                                        axis.ticks = element_blank())+
  # xlab("Longitude") + ylab("Latitude")+
  ggrepel::geom_text_repel(data= label.data.2,aes(x=long, y= lat, label=region),inherit.aes = F,
            color = "darkblue", fontface = "bold", stat = 'identity',
            position = "identity")

ggsave("Manuscript.figures/distribution.png", distribution, width = 12, height = 6, dpi = 600, bg ="white")

@@

A quantitative cross-sectional fully anonymous online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch). Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) of a Comic co-released with the survey[@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux]. The landing page of the on-line survey had the explanatory statements It was mentioned in the explanatory statement that their participation was voluntary and that they could withdraw from participation anytime without being penalized. At the beginning of the survey, for the adult participants (>18 years) consent was recorded digitally. Underaged participants (<18 years) were urged to obtain assent from their parents/legal guardians, before filling in the survey. The survey took around 15 to 20 minutes for which they were not compensated. As a part of the demographics participants provided information regarding age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language as single-item demographic variables. The demographic characteristics of our sample are given in Table \@ref(tab:demotab).To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention. What is 4+5?"). Participants needed to confirm that they were participating the survey for the first time. Questions incorporating retrospective recall were all aligned to the period of "past four weeks". At first we collected data for from `r nrow(EFA.descriptives)` participants (EFA sample). Next, we collected data from another `r nrow(CFA.descriptives)` participants (CFA sample) making a total sample of `r nrow(desctable.data)`. The data analysed in this study was collected between 17 May 2021 and 3 September 2021.

```{r demotab, warning=F, message=F}
desc_kable  %>% kable_styling(latex_options = c("scale_down")) %>% landscape()
```

@@

By reason of using fully anonymous online survey data, the present research project does not fall under the scope of the Human Research Act, making an authorisation from the ethics committee redundant. Nevertheless, the cantonal ethics commission (Ethikkommission Nordwest- und Zentralschweiz, EKNZ) reviewed our proposition (project ID Req-2021-00488) and issued an official clarification of responsibility.

@@

After reviewing the literature, we identified several light exposure related scale. However, no scales specifically measuring the behavioural component of light exposure were found (\@ref(tab:reltab2). As such, we developed a comprehensive item pool of 48 items. The whole list of 48 items were then judged  based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by an expert panel. The expert panel composed of all authors and researchers from the fields of chronobiology, light research, neuroscience and psychology. The panel members independently judged each of the items in terms of their relevance and representativeness and suggested required modification, if there is any. The author team acknowledged the suggestions and amended the items as required thus creating a 48-item scale

@@

Table \@ref(tab:demotab) summarizes the survey participants' demographic characteristics. Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses. (XX??) participants were excluded from analysis due to not passing at least one of the "attention check" items. For exploring initial factor structure (EFA), a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013].For estimating the sample size for the confirmatory factor analysis (CFA) we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per item is required to earn trustworthiness of the result. Our sample size exceeds these requirements.
We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones).
Participants reported a diverse range of geographic location
Participants indicated filling out the online survey from a diverse range of geographic locations. The ten most common country and time zone combinations included:

```{r fig.cap="Countries with Highest Responses", out.height= '100%', out.width= '100%'}
knitr::include_graphics('Manuscript.figures/distribution.png', dpi = 800 )
```
